Paper on the carbonate chemistry at Ny-Ålesund

### 2020-11-12 paper.Rmd

```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}

var_list <- c("sal_fb", "temp_fb")
n_na <- NULL
for (i in 1:length(var)) {
  na <- sum(!is.na([[i]]))
  a
}

pc_na <- function(x=df) {
  NAs <- as.tibble(map_df(x, function(x) sum(!is.na(x)))) %>% # number of NAs
    dplyr::select(-datetime)
  NAs <- as.data.frame(t(NAs))
  n <- nrow(x) # total number of rows
  pc_na <- n_na/n #fraction of NAs
  NAs$pc <- pc_na$V1
  return(NAs)
}
tmp <- d %>% 
  as_tibble() %>% 
  dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
                starts_with("temp_"), at_calc, year_month, quarter) %>%
  summarize()

>>>>

```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
zz <- d %>%
  group_by_key() %>%
  index_by(quarter = ~ quarter(.)) %>% # monthly aggregates
  summarise(
    sal_fb_na = sum(!is.na(sal_fb))/n())
zz

zz <- d %>%
  group_by_key() %>%
  index_by(year_month = ~ yearmonth(.)) %>% # monthly aggregates
  summarise(
    sal_fb_na = sum(!is.na(sal_fb))/n())
zz
